---
title: "Draft Quarto document"
author: "Julie Bjerrelund"
format: html
---

## Setup and maintain code

```{r setup}
library(tidyverse)
library(here)
library(snakecase) # snake case, all letters of the heading of the table will be low case letters separated by _. name_repair can update column names while we load it. more readable and best practice to use
```

## Importing new data 
```{r}
# here function, tells R to go back to where the project file is located.
# %>% Pipe, command, shift, P
# we only load in a small part of the dataset to actually be able to read it and see part of the dataset. we can use n_max to tell how many rows will be loaded
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  ) # only import 100 rows of the dataset
```

##Exercise: Reading other files 

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  )
```
```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
  )
```
```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  )
```


##Creating our first function, making a function to add numbers 
#This is the structure of a function:
#name <- function(argument1, argument2) 
# body of function, output <- ... return(output)

```{r}
#' Add two numbers together
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers (describe what the function returns)
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added) # this function should return this output
}
```

#Roxygen - a way to document what you are doing. you have to be somewhere within the function with the curser. Delete export and examples, only needed if you make a package 

## Import 5C's HR data with a function
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```
```{r}
#' Read in one nurses' stress data file.
#'
#' @param file_path A path to a data file
#'
#' @returns outputs a data frame /tibble
read <- function(file_path) {
  data <- file_path |> # this is the argument for the function, whatever path is put in, will be read in as a csv file.
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(data)
}
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read()
```
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read()
```

##Rewrite function code, so it can contain more or less rows.
```{r}
#' Read in one nurses' stress data file 
#'
#' @param file_path A path to data file
#' @param max_rows Maximum of rows to read
#'
#' @returns Dataframe

read <- function(file_path, max_rows=100) { #default argument, so if we dont specify max rows, this will be the default¨
  data <- file_path |> # this is the argument for the function, whatever path is put in, will be read in as a csv file.
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = max_rows
    )
  return(data)
}
```

```{r}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```
## DESCRIPTION FILE - where information about the project is written. metadata file found within a Rproject. We can add package to it in order for others and your self to know. e.g. we are dependent on the "here" packages
