---
title: "Draft Quarto document"
author: "Julie Bjerrelund"
format: html
---

## Setup and maintain code

```{r setup}
library(tidyverse)
library(here)
library(snakecase) # snake case, all letters of the heading of the table will be low case letters separated by _. name_repair can update column names while we load it. more readable and best practice to use
```

## Importing new data 
```{r}
# here function, tells R to go back to where the project file is located.
# %>% Pipe, command, shift, P
# we only load in a small part of the dataset to actually be able to read it and see part of the dataset. we can use n_max to tell how many rows will be loaded
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  ) # only import 100 rows of the dataset
```

##Exercise: Reading other files 

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```
```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  )
```
```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
  )
```
```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  )
```


##Creating our first function, making a function to add numbers 
#This is the structure of a function:
#name <- function(argument1, argument2) 
# body of function, output <- ... return(output)

```{r}
#' Add two numbers together
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers (describe what the function returns)
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added) # this function should return this output
}
```

#Roxygen - a way to document what you are doing. you have to be somewhere within the function with the curser. Delete export and examples, only needed if you make a package 

