---
title: "Draft Quarto document"
author: "Julie Bjerrelund"
format: html
---

## Setup and maintain code

```{r setup}
library(tidyverse)
library(here)
library(snakecase)
library(fs)
library(stringr)
source(here("R/functions.R"))
```

## Importing new data

```{r}
#|eval: false

# here function, tells R to go back to where the project file is located.
# %>% Pipe, command, shift, P
# we only load in a small part of the dataset to actually be able to read it and see part of the dataset. we can use n_max to tell how many rows will be loaded
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  ) # only import 100 rows of the dataset
```

##Exercise: Reading other files

```{r}
#|eval: false
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case
  )
```

```{r}
#|eval: false

here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  )
```

```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
  )
```

```{r}
here("data-raw/nurses-stress/stress/6B/6B_1587569373/EDA.csv.gz") %>%
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case, # printer ikke output af, hvad read_csv gætter på, at data er.
    n_max = 100
  )
```

##Creating our first function, making a function to add numbers #This is the structure of a function: #name \<- function(argument1, argument2) \# body of function, output \<- ... return(output)

```{r}
#' Add two numbers together
#'
#' @param num1 A number here.
#' @param num2 A number here.
#'
#' @returns Returns the sum of two numbers (describe what the function returns)
#'
add_numbers <- function(num1, num2) {
  added <- num1 + num2
  return(added) # this function should return this output
}
```

#Roxygen - a way to document what you are doing. you have to be somewhere within the function with the curser. Delete export and examples, only needed if you make a package

## Import 5C's HR data with a function

```{r}
#|eval: false

here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") |>
  read_csv(
    show_col_types = FALSE,
    name_repair = to_snake_case,
    n_max = 100
  )
```

```{r}
#|eval: false
#' Read in one nurses' stress data file.
#'
#' @param file_path A path to a data file
#'
#' @returns outputs a data frame /tibble
read <- function(file_path) {
  data <- file_path |> # this is the argument for the function, whatever path is put in, will be read in as a csv file.
    read_csv(
      show_col_types = FALSE,
      name_repair = to_snake_case,
      n_max = 100
    )
  return(data)
}
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886626/HR.csv.gz") %>%
  read()
```

```{r}
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") %>%
  read()
```

##Rewrite function code, so it can contain more or less rows.

```{r}
#|eval: false

#' Read in one nurses' stress data file
#'
#' @param file_path A path to data file
#' @param max_rows Maximum of rows to read
#'
#' @returns Dataframe

read <- function(file_path, max_rows = 100) { # default argument, so if we dont specify max rows, this will be the default¨
  data <- file_path |> # this is the argument for the function, whatever path is put in, will be read in as a csv file.
    readr::read_csv(
      show_col_types = FALSE,
      name_repair = snakecase::to_snake_case,
      n_max = max_rows
    )
  return(data)
}
```

```{r}
# Outputs only 100 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read()

# Outputs only 1000 rows
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = 1000)

# Outputs all rows (`Inf` means infinity)
here("data-raw/nurses-stress/stress/5C/5C_1586886712/HR.csv.gz") |>
  read(max_rows = Inf)
```

## DESCRIPTION FILE - where information about the project is written. metadata file found within a Rproject. We can add package to it in order for others and your self to know. e.g. we are dependent on the "here" packages.

# we do that with this code: usethis::use_package("here") in the consol. "here" refers to the package we are dependent on, will appear in the DESCRIPTION file.

##Day 2 - mapping/functionals \# we want to use map and thereby read in all 3000 files from the dataset. we need a list of all the filepaths we want

## Using map

```{r}
hr_files <- here("data-raw/nurses-stress/") %>%
  dir_ls(regexp = "HR.csv.gz", recurse = TRUE) # dir_ls er en måde at vise, hvilke filer der er i directory, altså den destination der anvendes til here functionen. Det printes ikke, med mindre der skrives hr_files til sidst i koden. recurse bruger vi, da alle filerne ikke er i den samme mappe, det er en måde at kigge i alle undermapperne.
```

```{r}
hr_data <- hr_files %>%
  map(read) # NO BRACKETS here

hr_data
```

#We want to combine the data to get one dataframe, either row or column bind - we want to bind rows, because columns are the same for all the nurses

```{r}
hr_data <- hr_files %>%
  map(read) %>%
  list_rbind(names_to = "file_path_id") # to list who is who

hr_data
```

## Exercise: Convert map to function and use on sleep

```{r}
#' Function to read in an combine all data
#'
#' @param Name of the files in the sub-folder we want to read in data from
#'
#' @returns A combined tibble with wanted data

read_all <- function(filename) {
  files <- here::here("data-raw/nurses-stress/") %>%
    fs::dir_ls(regexp = filename, recurse = TRUE) # indlæser alle filerne

  data <- files %>%
    purrr::map(read) %>%
    purrr::list_rbind(names_to = "file_path_id") # binder alle filerne sammen og opdeler på file ID, som lige nu er lidt for langt, men det bliver korrigeret ved næste session

  return(data)
}

hr_data <- read_all("HR.csv.gz")
IBI_data <- read_all("IBI.csv.gz")
```

## Inspecting the data

```{r}
hr_data <- read_all("HR.csv.gz")

survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") |>
  read()

hr_data
survey_data
```

```{r}
hr_data %>%
  mutate(
    id = str_extract(
      file_path_id,
      pattern = "/stress/[:alnum:]{2}/" # alnum finder både bogstaver og tal, 2 angiver at der skal være to tegn, fx 15 eller 5C.
    ) %>%
      str_remove("/stress/") %>%
      str_remove("/"),
    .before = file_path_id # telling us how are columns are organised.
  ) %>%
  select(-file_path_id)
```

```{r}
#| eval: false
get_participant_id <- function(data) {
  data_with_id <- data %>%
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        "/stress/[[:alnum:]]{2}/"
      ) %>%
        stringr::str_remove("/stress/") %>%
        stringr::str_remove("/"),
      .before = file_path_id
    ) %>%
    dplyr::select(-file_path_id)

  return(data_with_id)
}
```

# Use lookaround from the stringr in order to get rid of /stress/ and / at the beginning, a more simple code:

```{r}
get_participant_id <- function(data) {
  data_with_id <- data |>
    dplyr::mutate(
      id = stringr::str_extract(
        file_path_id,
        "(?<=/stress/)[:alnum:]{2}(?=/)"
      ),
      .before = file_path_id
    ) |>
    dplyr::select(-file_path_id)
  return(data_with_id)
}
```

##Working with across

```{r}
hr_data <- read_all("HR.csv.gz") %>%
  get_participant_id()

hr_data
```

```{r}
hr_data |>
  summarise(across(where(is.numeric), list(
    mean = mean,
    median = median,
    sd = sd
  )))
```

##Working with dates

```{r}
hr_data %>%
  mutate(
    datetime = round_date(collection_datetime,
      unit = "minute"
    ),
    .before = "collection_datetime"
  )
```

##Summarising by groups

```{r}
hr_data |>
  mutate(
    collection_datetime = lubridate::round_date(
      collection_datetime,
      unit = "minute"
    )
  ) |>
  summarise(
    across(
      where(is.numeric),
      list(mean = mean, sd = sd, median = median)
    ),
    .by = c(id, collection_datetime) # this is group by, we use c. because we want combination
  )
```

```{r}
#' Summarise data in a tibble with rounded timepoints
#'
#' @param Dataframe with collection_datetime and columns
#'
#' @returns Tibble, summarised dataframe

summarise_by_datetime <- function(data) {
  summarised_data <- data |>
    dplyr::mutate(
      collection_datetime = lubridate::round_date(
        collection_datetime,
        unit = "minute"
      )
    ) |>
    dplyr::summarise(
      dplyr::across(
        tidyselect::where(is.numeric),
        list(mean = mean, sd = sd, median = median)
      ),
      .by = c(id, collection_datetime)
    )
  return(summarised_data)
}
```

##Pivot longer

```{r}
survey_data <- here("data-raw/nurses-stress/survey-results.csv.gz") %>%
  read()
survey_data
```

```{r}
survey_tidy <- survey_data |>
  mutate(
    date = mdy(date),
    start_datetime = as_datetime(paste(date, start_time)),
    end_datetime = as_datetime(paste(date, end_time)),
    datetime_id = start_datetime,
    .before = start_time
  ) %>%
  select(-c(date, start_time, end_time, duration))

survey_tidy
```

```{r}
survey_tidy %>%
  select(id, datetime_id, start_datetime, end_datetime) %>%
  pivot_longer(c(start_datetime, end_datetime), names_to = NULL, values_to = "collection_datetime") %>%
  group_by(pick(-collection_datetime)) %>%
  complete(collection_datetime = seq(min(collection_datetime),
    max(collection_datetime),
    by = 60
  )) %>%
  ungroup()
```

```{r}
#' Tidy data from the survey
#'
#' @param Dataframe with survey data matching timestamps from HR dataset
#'
#' @returns Dataframe

tidy_survey_dates <- function(data) {
  tidied <- data |>
    dplyr::mutate(
      date = lubridate::mdy(date),
      start_datetime = lubridate::as_datetime(paste(date, start_time)),
      end_datetime = lubridate::as_datetime(paste(date, end_time)),
      datetime_id = start_datetime,
      .before = start_time
    ) %>%
    dplyr::select(-c(date, start_time, end_time, duration))

  return(tidied)
}
```


```{r}
#' Pivot longer the dataset with only id and datetime
#'
#' @param dataframe
#'
#' @returns long dataframe

survey_to_long <- function(data) {
  longer <- data %>%
    dplyr::select(id, datetime_id, start_datetime, end_datetime) %>%
    tidyr::pivot_longer(
      c(start_datetime, end_datetime),
      names_to = NULL,
      values_to = "collection_datetime"
    ) %>%
    dplyr::group_by(pick(-collection_datetime)) %>%
    tidyr::complete(
      collection_datetime = seq(
        min(collection_datetime),
        max(collection_datetime),
        by = 60
      )
    ) %>%
    dplyr::ungroup()

  return(longer)
}
```
